---
title: "renv (plus git) setup"
author: "Richard Ramsey"
date: "02/05/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This file tries to test the renv package to see how it works and how it could be incorporated into one's workflow. And also link it to a version control system (git).

It follows these:

https://www.youtube.com/watch?v=yjlEbIDevOs

https://kevinushey-2020-rstudio-conf.netlify.app/slides.html#146

## install renv ##

only necessary once.

```{r install-renv}
# install.packages("renv")
```

## initialise renv ##

```{r initialise-renv}
# renv::init()
```

## load packages that we will be using ##

```{r dependencies, echo=TRUE, message=FALSE, warning=FALSE}
# initialise renv
# renv::init() ## note - if you've setup renv in RStudio by ticking the appropriate box, this line might be unnecessary.

# install or load packages
options(repos="https://cran.rstudio.com" )
if (!require("install.load")){install.packages("install.load")} 
install_load("here", "tidyverse", "RColorBrewer", "patchwork", "brms")

# take a snapshot and update the lock.file
# renv::snapshot()
```

## take a snapshot and update the lockfile ##

```{r}
renv::snapshot()
```

## try the renv::restore function ##

```{r}
renv::restore()
```

## do some coding ##

```{r load-some-data}
data <- as_tibble(mtcars) %>% 
  mutate(cyl = factor(cyl))
head(data)
str(data)
```

## plot some stuff ##

```{r plot}
p1 <- ggplot(data, 
             aes(x=hp, y=mpg, colour=cyl, shape=cyl)) +
  geom_point() +
  theme_bw() +
  scale_colour_brewer(palette = "Dark2") +
  facet_wrap(~cyl)
p1

ggsave("figures/p1.jpeg")
```

## run a simple model using brms ##

```{r}
b1 <- brm(mpg ~ 1 + hp,
          data = data, family = gaussian,
          file = "models/b1")
summary(b1)
```


## print session info ##

```{r session-info}
sessionInfo()
```

